```{r}
library(MatchIt)
library(tidyverse)
library(cobalt)
library(lubridate)
library(data.table)
library(stargazer)
# library(dummies)
restaurants <- read_csv("../Data/All_restaurants_finalized.csv")
reviews <- read_csv("../Data/reviews(new).csv")
```
```{r}
file <- "Third_parties_match(period=730 days, 0/00/00, min_num=30).csv"
file_1 <- "lowvalue_highsub(restaurants).csv"
file_2 <- "highvalue_highsub(restaurants).csv"
file_3 <- "lowvalue_lowsub(restaurants).csv"
file_4 <- "highvalue_lowsub(restaurants).csv"
caliper <- 0.3
ratio <- 3
time <- ymd("2017-2-28")
first_time_group <- c("Applebee's", "O'Charley's", "Rainforest Cafe", "Cheddar's Scratch Kitchen", "Bubba Gump Shrimp", "Saltgrass Steak House", "Dave & Buster's", "California Pizza Kitchen")

period_vector <- c()
min_num_vector <- c()
measure_vector <- c()
observation_vector <- c()
formula_vector <- c()
ratio_vector <- c()
caliper_vector <- c()
p1_vector <- c()
p2_vector <- c()
p3_vector <- c()
b1_vector <- c()
b2_vector <- c()
b3_vector <- c()
r1_vector <- c()
r2_vector <- c()
r3_vector <- c()
p4_vector <- c()
p5_vector <- c()
p6_vector <- c()
b4_vector <- c()
b5_vector <- c()
b6_vector <- c()
r4_vector <- c()
r5_vector <- c()
r6_vector <- c()
no1_vector <- c()
no2_vector <- c()
no3_vector <- c()


ratio_vector <- c(ratio_vector, ratio)
caliper_vector <- c(caliper_vector, caliper)

# Low value & High sub
data <- read_csv(paste("../Data/", file_1, sep=""))
period <- substr(file_1, 28, 30)
period <- ddays(as.numeric(730))
min_num <- substr(file_1, 55, 56)
period_vector <- c(period_vector, period)
min_num_vector <- c(min_num_vector, min_num)

data$Treated <- ifelse(data$Treated_Yelp == "Y", 1, 0)

new_data <- dplyr::select(data, ID, Lat, Long, Treated, Zip, Review_count_before, Review_count_after, Rating_before, Rating_after, City_code, Match)
new_data <- as.data.frame(na.omit(new_data))
set.seed(100)
m.out <- matchit(Treated ~ Review_count_before + Rating_before, data = new_data, ratio=ratio, discard="both", method="nearest", exact=c("Match"), caliper=caliper)
model_result <- bal.tab(m.out, s.d.denom="pooled", disp.v.ratio=TRUE)
measure <- toString(model_result[1])
observations <- toString(model_result[2])
formula <- toString(model_result[3])
measure_vector <- c(measure_vector, measure)
observation_vector <- c(observation_vector, observations)
formula_vector <- c(formula_vector, formula)

matches <- m.out$match.matrix
matches_df <- data.frame(cbind(row.names(matches), matches))
df_regression <- data.frame()
for (row in 1:nrow(matches_df)){
  if (is.na(matches_df[row, 2])){
    next
  }
  ID_treated <- data[matches_df[row, 1], "ID"]
  name <- restaurants[which(restaurants$ID==toString(ID_treated)), "Name"]
  df_treated <- reviews[which(reviews$ID==toString(ID_treated) & reviews$timestamps<=time+period & reviews$timestamps>=time-period), ]
  df_treated[, paste("Pair", toString(row), sep="")] <- 1
  for (index in matches_df[row, 2:(ratio+1)]){
    if (is.na(index)){
      next
    } else {
      ID_control <- data[as.numeric(index), "ID"]
      df_control <- reviews[which(reviews$ID==toString(ID_control) & reviews$timestamps<=time+period & reviews$timestamps>=time-period), ]
      df_control[, paste("Pair", toString(row), sep="")] <- 1
      df_treated <- rbind(setDT(df_treated), setDT(df_control), fill=TRUE)
      df_treated[, "First_time"] <- as.numeric(name %in% first_time_group)
      df_regression <- rbind(setDT(df_regression), setDT(df_treated), fill=TRUE)
    }
  }
}
df_regression[is.na(df_regression)] <- 0
df_regression$After <- unlist(lapply(df_regression$timestamps, function(x) as.numeric(x>time)))
df_regression$Treated <- unlist(lapply(df_regression$Control, function(x) as.numeric(x=="N")))
df_regression$Treated_X_After <- df_regression$After * df_regression$Treated
df_regression$elite <- unlist(lapply(df_regression$elite, function(x) as.numeric(x=="Y")))
df_regression_1 <- df_regression[which(df_regression$First_time==1),]
df_regression_2 <- df_regression[which(df_regression$First_time==0),]
no1_vector <- c(no1_vector, nrow(df_regression_1))
no2_vector <- c(no2_vector, nrow(df_regression_2))
no3_vector <- c(no3_vector, nrow(df_regression))

print("LH:")
print(sum(df_regression_1$Treated))
print(length(df_regression_1$Treated) - sum(df_regression_1$Treated))
print("Control:")
print(summary(m.out)$nn["Matched", "Control"])
print("Treated:")
print(summary(m.out)$nn["Matched", "Treated"])
print("Number of chains(Treated): ")
print(length(unique(df_regression_1[which(df_regression_1$Treated == 1), ]$Name)))
print("Number of chains(Control): ")
print(length(unique(df_regression_1[which(df_regression_1$Treated == 0), ]$Name)))

#One Hot Encoding
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, "'", "")}))
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, "&", "")}))
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, "-", "")}))
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, " ", "_")}))
orig_vars = c("After", "Treated", "Treated_X_After", "nfriends", "useful", "elite", "nphotos_review", "checkin", "Fog_index", "Avg_word_length", "Subjectivity", "Sent_length", "Food_quality", "Atmosphere")
# new_vars = paste("Name_", unique(df_regression_1$Name), sep="")
# vars = c(orig_vars, new_vars)
vars = orig_vars

# df_regression_1 = dummy.data.frame(df_regression_1, names=c("Name"), sep="_")

#line
fmla = as.formula(paste("complain_line ~ ", paste(vars, collapse="+")))
if (nrow(df_regression_1)>0){
  model1 <- glm(fmla, data = df_regression_1, family = "binomial")
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
}

#service
#line
fmla = as.formula(paste("complain_service ~ ", paste(vars, collapse="+")))
if (nrow(df_regression_1)>0){
  model2 <- glm(fmla, data = df_regression_1, family = "binomial")
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
}

#ratings
fmla = as.formula(paste("ratings ~ ", paste(vars, collapse="+")))
if (nrow(df_regression_1)>0){
  model3 <- glm(fmla, data = df_regression_1, family = "gaussian")
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
}


# High Value & High Sub
data <- read_csv(paste("../Data/", file_2, sep=""))
period <- substr(file, 28, 30)
period <- ddays(as.numeric(730))
min_num <- substr(file, 55, 56)
period_vector <- c(period_vector, period)
min_num_vector <- c(min_num_vector, min_num)

data$Treated <- ifelse(data$Treated_Yelp == "Y", 1, 0)
new_data <- dplyr::select(data, ID, Lat, Long, Treated, Zip, Review_count_before, Review_count_after, Rating_before, Rating_after, City_code, Match)
new_data <- as.data.frame(na.omit(new_data))
set.seed(100)
m.out <- matchit(Treated ~ Review_count_before + Rating_before, data = new_data, ratio=ratio, discard="both", method="nearest", exact=c("Match"), caliper=caliper)
model_result <- bal.tab(m.out, s.d.denom="pooled", disp.v.ratio=TRUE)
measure <- toString(model_result[1])
observations <- toString(model_result[2])
formula <- toString(model_result[3])
measure_vector <- c(measure_vector, measure)
observation_vector <- c(observation_vector, observations)
formula_vector <- c(formula_vector, formula)

matches <- m.out$match.matrix
matches_df <- data.frame(cbind(row.names(matches), matches))
df_regression <- data.frame()
for (row in 1:nrow(matches_df)){
  if (is.na(matches_df[row, 2])){
    next
  }
  ID_treated <- data[matches_df[row, 1], "ID"]
  name <- restaurants[which(restaurants$ID==toString(ID_treated)), "Name"]
  df_treated <- reviews[which(reviews$ID==toString(ID_treated) & reviews$timestamps<=time+period & reviews$timestamps>=time-period), ]
  df_treated[, paste("Pair", toString(row), sep="")] <- 1
  for (index in matches_df[row, 2:(ratio+1)]){
    if (is.na(index)){
      next
    } else {
      ID_control <- data[as.numeric(index), "ID"]
      df_control <- reviews[which(reviews$ID==toString(ID_control) & reviews$timestamps<=time+period & reviews$timestamps>=time-period), ]
      df_control[, paste("Pair", toString(row), sep="")] <- 1
      df_treated <- rbind(setDT(df_treated), setDT(df_control), fill=TRUE)
      df_treated[, "First_time"] <- as.numeric(name %in% first_time_group)
      df_regression <- rbind(setDT(df_regression), setDT(df_treated), fill=TRUE)
    }
  }
}
df_regression[is.na(df_regression)] <- 0
df_regression$After <- unlist(lapply(df_regression$timestamps, function(x) as.numeric(x>time)))
df_regression$Treated <- unlist(lapply(df_regression$Control, function(x) as.numeric(x=="N")))
df_regression$Treated_X_After <- df_regression$After * df_regression$Treated
df_regression$elite <- unlist(lapply(df_regression$elite, function(x) as.numeric(x=="Y")))
df_regression_1 <- df_regression[which(df_regression$First_time==1),]
df_regression_2 <- df_regression[which(df_regression$First_time==0),]
no1_vector <- c(no1_vector, nrow(df_regression_1))
no2_vector <- c(no2_vector, nrow(df_regression_2))
no3_vector <- c(no3_vector, nrow(df_regression))

print("HH:")
print(sum(df_regression_1$Treated))
print(length(df_regression_1$Treated) - sum(df_regression_1$Treated))
print("Control:")
print(summary(m.out)$nn["Matched", "Control"])
print("Treated:")
print(summary(m.out)$nn["Matched", "Treated"])
print("Number of chains(Treated): ")
print(length(unique(df_regression_1[which(df_regression_1$Treated == 1), ]$Name)))
print("Number of chains(Control): ")
print(length(unique(df_regression_1[which(df_regression_1$Treated == 0), ]$Name)))

#One Hot Encoding
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, "'", "")}))
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, "&", "")}))
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, "-", "")}))
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, " ", "_")}))
orig_vars = c("After", "Treated", "Treated_X_After", "nfriends", "useful", "elite", "nphotos_review", "checkin", "Fog_index", "Avg_word_length", "Subjectivity", "Sent_length", "Food_quality", "Atmosphere")
# new_vars = paste("Name_", unique(df_regression_1$Name), sep="")
# vars = c(orig_vars, new_vars)
vars = orig_vars

# df_regression_1 = dummy.data.frame(df_regression_1, names=c("Name"), sep="_")

#line
fmla = as.formula(paste("complain_line ~ ", paste(vars, collapse="+")))
if (nrow(df_regression_1)>0){
  model4 <- glm(fmla, data = df_regression_1, family = "binomial")
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
}

#service
#line
fmla = as.formula(paste("complain_service ~ ", paste(vars, collapse="+")))
if (nrow(df_regression_1)>0){
  model5 <- glm(fmla, data = df_regression_1, family = "binomial")
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
}

#ratings
fmla = as.formula(paste("ratings ~ ", paste(vars, collapse="+")))
if (nrow(df_regression_1)>0){
  model6 <- glm(fmla, data = df_regression_1, family = "gaussian")
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
}


# Low Value & Low Sub
data <- read_csv(paste("../Data/", file_3, sep=""))
period <- substr(file, 28, 30)
period <- ddays(as.numeric(730))
min_num <- substr(file, 55, 56)
period_vector <- c(period_vector, period)
min_num_vector <- c(min_num_vector, min_num)
data$Treated <- ifelse(data$Treated_Yelp == "Y", 1, 0)

new_data <- dplyr::select(data, ID, Lat, Long, Treated, Zip, Review_count_before, Review_count_after, Rating_before, Rating_after, City_code, Match)
new_data <- as.data.frame(na.omit(new_data))
set.seed(100)
m.out <- matchit(Treated ~ Review_count_before + Rating_before, data = new_data, ratio=ratio, discard="both", method="nearest", exact=c("Match"), caliper=caliper)
model_result <- bal.tab(m.out, s.d.denom="pooled", disp.v.ratio=TRUE)
measure <- toString(model_result[1])
observations <- toString(model_result[2])
formula <- toString(model_result[3])
measure_vector <- c(measure_vector, measure)
observation_vector <- c(observation_vector, observations)
formula_vector <- c(formula_vector, formula)

matches <- m.out$match.matrix
matches_df <- data.frame(cbind(row.names(matches), matches))
df_regression <- data.frame()
for (row in 1:nrow(matches_df)){
  if (is.na(matches_df[row, 2])){
    next
  }
  ID_treated <- data[matches_df[row, 1], "ID"]
  name <- restaurants[which(restaurants$ID==toString(ID_treated)), "Name"]
  df_treated <- reviews[which(reviews$ID==toString(ID_treated) & reviews$timestamps<=time+period & reviews$timestamps>=time-period), ]
  df_treated[, paste("Pair", toString(row), sep="")] <- 1
  for (index in matches_df[row, 2:(ratio+1)]){
    if (is.na(index)){
      next
    } else {
      ID_control <- data[as.numeric(index), "ID"]
      df_control <- reviews[which(reviews$ID==toString(ID_control) & reviews$timestamps<=time+period & reviews$timestamps>=time-period), ]
      df_control[, paste("Pair", toString(row), sep="")] <- 1
      df_treated <- rbind(setDT(df_treated), setDT(df_control), fill=TRUE)
      df_treated[, "First_time"] <- as.numeric(name %in% first_time_group)
      df_regression <- rbind(setDT(df_regression), setDT(df_treated), fill=TRUE)
    }
  }
}
df_regression[is.na(df_regression)] <- 0
df_regression$After <- unlist(lapply(df_regression$timestamps, function(x) as.numeric(x>time)))
df_regression$Treated <- unlist(lapply(df_regression$Control, function(x) as.numeric(x=="N")))
df_regression$Treated_X_After <- df_regression$After * df_regression$Treated
df_regression$elite <- unlist(lapply(df_regression$elite, function(x) as.numeric(x=="Y")))
df_regression_1 <- df_regression[which(df_regression$First_time==1),]
df_regression_2 <- df_regression[which(df_regression$First_time==0),]
no1_vector <- c(no1_vector, nrow(df_regression_1))
no2_vector <- c(no2_vector, nrow(df_regression_2))
no3_vector <- c(no3_vector, nrow(df_regression))

print("LL:")
print(sum(df_regression_1$Treated))
print(length(df_regression_1$Treated) - sum(df_regression_1$Treated))
print("Control:")
print(summary(m.out)$nn["Matched", "Control"])
print("Treated:")
print(summary(m.out)$nn["Matched", "Treated"])
print("Number of chains(Treated): ")
print(length(unique(df_regression_1[which(df_regression_1$Treated == 1), ]$Name)))
print("Number of chains(Control): ")
print(length(unique(df_regression_1[which(df_regression_1$Treated == 0), ]$Name)))

#One Hot Encoding
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, "'", "")}))
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, "&", "")}))
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, "-", "")}))
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, " ", "_")}))
orig_vars = c("After", "Treated", "Treated_X_After", "nfriends", "useful", "elite", "nphotos_review", "checkin", "Fog_index", "Avg_word_length", "Subjectivity", "Sent_length", "Food_quality", "Atmosphere")
# new_vars = paste("Name_", unique(df_regression_1$Name), sep="")
# vars = c(orig_vars, new_vars)
vars = orig_vars

# df_regression_1 = dummy.data.frame(df_regression_1, names=c("Name"), sep="_")

#line
fmla = as.formula(paste("complain_line ~ ", paste(vars, collapse="+")))
if (nrow(df_regression_1)>0){
  model7 <- glm(fmla, data = df_regression_1, family = "binomial")
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
}

#service
#line
fmla = as.formula(paste("complain_service ~ ", paste(vars, collapse="+")))
if (nrow(df_regression_1)>0){
  model8 <- glm(fmla, data = df_regression_1, family = "binomial")
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
}

#ratings
fmla = as.formula(paste("ratings ~ ", paste(vars, collapse="+")))
if (nrow(df_regression_1)>0){
  model9 <- glm(fmla, data = df_regression_1, family = "gaussian")
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
}


#High Value & Low Sub
data <- read_csv(paste("../Data/", file_4, sep=""))
period <- substr(file, 28, 30)
period <- ddays(as.numeric(730))
min_num <- substr(file, 55, 56)
period_vector <- c(period_vector, period)
min_num_vector <- c(min_num_vector, min_num)
data$Treated <- ifelse(data$Treated_Yelp == "Y", 1, 0)

new_data <- dplyr::select(data, ID, Lat, Long, Treated, Zip, Review_count_before, Review_count_after, Rating_before, Rating_after, City_code, Match)
new_data <- as.data.frame(na.omit(new_data))
set.seed(100)
m.out <- matchit(Treated ~ Review_count_before + Rating_before, data = new_data, ratio=ratio, discard="both", method="nearest", exact=c("Match"), caliper=caliper)
model_result <- bal.tab(m.out, s.d.denom="pooled", disp.v.ratio=TRUE)
measure <- toString(model_result[1])
observations <- toString(model_result[2])
formula <- toString(model_result[3])
measure_vector <- c(measure_vector, measure)
observation_vector <- c(observation_vector, observations)
formula_vector <- c(formula_vector, formula)

matches <- m.out$match.matrix
matches_df <- data.frame(cbind(row.names(matches), matches))
df_regression <- data.frame()
for (row in 1:nrow(matches_df)){
  if (is.na(matches_df[row, 2])){
    next
  }
  ID_treated <- data[matches_df[row, 1], "ID"]
  name <- restaurants[which(restaurants$ID==toString(ID_treated)), "Name"]
  df_treated <- reviews[which(reviews$ID==toString(ID_treated) & reviews$timestamps<=time+period & reviews$timestamps>=time-period), ]
  df_treated[, paste("Pair", toString(row), sep="")] <- 1
  for (index in matches_df[row, 2:(ratio+1)]){
    if (is.na(index)){
      next
    } else {
      ID_control <- data[as.numeric(index), "ID"]
      df_control <- reviews[which(reviews$ID==toString(ID_control) & reviews$timestamps<=time+period & reviews$timestamps>=time-period), ]
      df_control[, paste("Pair", toString(row), sep="")] <- 1
      df_treated <- rbind(setDT(df_treated), setDT(df_control), fill=TRUE)
      df_treated[, "First_time"] <- as.numeric(name %in% first_time_group)
      df_regression <- rbind(setDT(df_regression), setDT(df_treated), fill=TRUE)
    }
  }
}
df_regression[is.na(df_regression)] <- 0
df_regression$After <- unlist(lapply(df_regression$timestamps, function(x) as.numeric(x>time)))
df_regression$Treated <- unlist(lapply(df_regression$Control, function(x) as.numeric(x=="N")))
df_regression$Treated_X_After <- df_regression$After * df_regression$Treated
df_regression$elite <- unlist(lapply(df_regression$elite, function(x) as.numeric(x=="Y")))
df_regression_1 <- df_regression[which(df_regression$First_time==1),]
df_regression_2 <- df_regression[which(df_regression$First_time==0),]
no1_vector <- c(no1_vector, nrow(df_regression_1))
no2_vector <- c(no2_vector, nrow(df_regression_2))
no3_vector <- c(no3_vector, nrow(df_regression))

print("HL:")
print(sum(df_regression_1$Treated))
print(length(df_regression_1$Treated) - sum(df_regression_1$Treated))
print("Control:")
print(summary(m.out)$nn["Matched", "Control"])
print("Treated:")
print(summary(m.out)$nn["Matched", "Treated"])
print("Number of chains(Treated): ")
print(length(unique(df_regression_1[which(df_regression_1$Treated == 1), ]$Name)))
print("Number of chains(Control): ")
print(length(unique(df_regression_1[which(df_regression_1$Treated == 0), ]$Name)))

#One Hot Encoding
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, "'", "")}))
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, "&", "")}))
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, "-", "")}))
df_regression_1$Name = unlist(lapply(df_regression_1$Name, function (x) {str_replace_all(x, " ", "_")}))
orig_vars = c("After", "Treated", "Treated_X_After", "nfriends", "useful", "elite", "nphotos_review", "checkin", "Fog_index", "Avg_word_length", "Subjectivity", "Sent_length", "Food_quality", "Atmosphere")
#new_vars = paste("Name_", unique(df_regression_1$Name), sep="")
#vars = c(orig_vars, new_vars)
vars = orig_vars
# df_regression_1 = dummy.data.frame(df_regression_1, names=c("Name"), sep="_")

#line
fmla = as.formula(paste("complain_line ~ ", paste(vars, collapse="+")))
if (nrow(df_regression_1)>0){
  model10 <- glm(fmla, data = df_regression_1, family = "binomial")
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
}

#service
#line
fmla = as.formula(paste("complain_service ~ ", paste(vars, collapse="+")))
if (nrow(df_regression_1)>0){
  model11 <- glm(fmla, data = df_regression_1, family = "binomial")
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
}

#ratings
fmla = as.formula(paste("ratings ~ ", paste(vars, collapse="+")))
if (nrow(df_regression_1)>0){
  model12 <- glm(fmla, data = df_regression_1, family = "gaussian")
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
}


```
dep.var.labels=c("Low Perceived Value & High Substitutability","High Perceived Value & High Substitutability", "Low Perceived Value & Low Substitutability", "High Perceived Value & Low Substitutability")
```{r}
stargazer(model3, model6, model9, model12, title="Subsample Results", column.labels = c("Low Value and High Substitutability","High Value and \\ High Substitutability", "Low Value and \\ Low Substitutability", "High Value and \\ Low Substitutability"),  omit.stat=c("LL","ser","f"), no.space = TRUE, column.sep.width = "1pt", star.cutoffs = c(.05, .01, .001), font.size = "small" )
```


```{r}
stargazer(model1, model4, model7, model10, title="Subsample Results", column.labels = c("Low Value and High Substitutability","High Value and \\ High Substitutability", "Low Value and \\ Low Substitutability", "High Value and \\ Low Substitutability"),  omit.stat=c("LL","ser","f"), no.space = TRUE, column.sep.width = "1pt", star.cutoffs = c(.05, .01, .001), font.size = "small" )
```

```{r}
stargazer(model2, model5, model8, model11, title="Subsample Results", column.labels = c("Low Value and High Substitutability","High Value and \\ High Substitutability", "Low Value and \\ Low Substitutability", "High Value and \\ Low Substitutability"),  omit.stat=c("LL","ser","f"), no.space = TRUE, column.sep.width = "1pt", star.cutoffs = c(.05, .01, .001), font.size = "small" )
```

summary(mod

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

