```{r}
library(MatchIt)
library(tidyverse)
library(cobalt)
library(lubridate)
restaurants <- read_csv("All_restaurants_finalized.csv")
reviews <- read_csv("reviews(processed).csv")
```
```{r}
file_list <- list.files(path="Third_party/")
caliper_list <- c(0.2, 0.25, 0.3, 0.35, 0.4)
ratio_max <- 10
time <- ymd("2017-2-28")
first_time_group <- c("Applebee's", "O'Charley's", "Rainforest Cafe", "Cheddar's Scratch Kitchen", "Bubba Gump Shrimp", "Saltgrass Steak House", "Dave & Buster's", "California Pizza Kitchen")
```

```{r}
period_vector <- c()
min_num_vector <- c()
measure_vector <- c()
observation_vector <- c()
formula_vector <- c()
ratio_vector <- c()
caliper_vector <- c()
p1_vector_1 <- c()
p1_vector_2 <- c()
p1_vector_3 <- c()
p2_vector_1 <- c()
p2_vector_2 <- c()
p2_vector_3 <- c()
p3_vector_1 <- c()
p3_vector_2 <- c()
p3_vector_3 <- c()
b1_vector_1 <- c()
b1_vector_2 <- c()
b1_vector_3 <- c()
b2_vector_1 <- c()
b2_vector_2 <- c()
b2_vector_3 <- c()
b3_vector_1 <- c()
b3_vector_2 <- c()
b3_vector_3 <- c()
r1_vector <- c()
r2_vector <- c()
r3_vector <- c()
p4_vector_1 <- c()
p4_vector_2 <- c()
p4_vector_3 <- c()
p5_vector_1 <- c()
p5_vector_2 <- c()
p5_vector_3 <- c()
p6_vector_1 <- c()
p6_vector_2 <- c()
p6_vector_3 <- c()
b4_vector_1 <- c()
b4_vector_2 <- c()
b4_vector_3 <- c()
b5_vector_1 <- c()
b5_vector_2 <- c()
b5_vector_3 <- c()
b6_vector_1 <- c()
b6_vector_2 <- c()
b6_vector_3 <- c()
r4_vector <- c()
r5_vector <- c()
r6_vector <- c()
v1_vector <- c()
v2_vector <- c()
v3_vector <- c()
v4_vector <- c()
v5_vector <- c()
v6_vector <- c()
no1_vector <- c()
no2_vector <- c()
no3_vector <- c()


#ratio_vector <- c(ratio_vector, ratio)
#caliper_vector <- c(caliper_vector, caliper)

file <- "Third_party/Third_parties_match(period=730 days,min_num=30).csv"
caliper <- 0.3
ratio <- 2
data <- read_csv(file)
period <- substr(file, 28, 30)
period <- ddays(as.numeric(period))
min_num <- substr(file, 55, 56)
period_vector <- c(period_vector, period)
min_num_vector <- c(min_num_vector, min_num)

new_data <- dplyr::select(data, ID, Lat, Long, Treated, Zip, Review_count_before, Review_count_after, Rating_before, Rating_after, City_code, Match)
new_data <- as.data.frame(na.omit(new_data))
set.seed(100)
m.out <- matchit(Treated ~ Review_count_before + Rating_before, data = new_data, ratio=ratio, discard="both", method="nearest", exact=c("Match", "City_code"), caliper=caliper)
model_result <- bal.tab(m.out, s.d.denom="pooled", disp.v.ratio=TRUE)
measure <- toString(model_result[1])
observations <- toString(model_result[2])
formula <- toString(model_result[3])
measure_vector <- c(measure_vector, measure)
observation_vector <- c(observation_vector, observations)
formula_vector <- c(formula_vector, formula)

matches <- m.out$match.matrix
matches_df <- data.frame(cbind(row.names(matches), matches))
df_regression <- data.frame()
for (row in 1:nrow(matches_df)){
  if (is.na(matches_df[row, 2])){
    next
  }
  ID_treated <- data[matches_df[row, 1], "ID"]
  name <- restaurants[which(restaurants$ID==toString(ID_treated)), "Name"]
  df_treated <- reviews[which(reviews$ID==toString(ID_treated) & reviews$timestamps<=time+dyears(2) & reviews$timestamps>=time-dyears(2)), ]
  df_treated[, paste("Pair", toString(row), sep="")] <- 1
  for (index in matches_df[row, 2:(ratio+1)]){
    if (is.na(index)){
      next
    } else {
      ID_control <- data[as.numeric(index), "ID"]
      df_control <- reviews[which(reviews$ID==toString(ID_control) & reviews$timestamps<=time+dyears(2) & reviews$timestamps>=time-dyears(2)), ]
      df_control[, paste("Pair", toString(row), sep="")] <- 1
      df_treated <- rbind(setDT(df_treated), setDT(df_control), fill=TRUE)
      df_treated[, "First_time"] <- as.numeric(name %in% first_time_group)
      df_regression <- rbind(setDT(df_regression), setDT(df_treated), fill=TRUE)
    }
  }
}
df_regression[is.na(df_regression)] <- 0
df_regression$After_1 <- unlist(lapply(df_regression$timestamps, function(x) as.numeric(x>time & x<(time + dyears(x = 2)))))
df_regression$After_2 <- unlist(lapply(df_regression$timestamps, function(x) as.numeric(x>(time + dyears(x = 1)) & x<(time + dyears(x = 2)))))
#df_regression$After_3 <- unlist(lapply(df_regression$timestamps, function(x) as.numeric(x>(time + dyears(x = 2)) & x<(time + dyears(x = 3)))))
df_regression$Treated <- unlist(lapply(df_regression$Control, function(x) as.numeric(x=="N")))
df_regression$Treated_X_After1 <- df_regression$After_1 * df_regression$Treated
df_regression$Treated_X_After2 <- df_regression$After_2 * df_regression$Treated
#df_regression$Treated_X_After3 <- df_regression$After_3 * df_regression$Treated
df_regression$elite <- unlist(lapply(df_regression$elite, function(x) as.numeric(x=="Y")))

df_regression_1 <- df_regression[which(df_regression$First_time==1),]
df_regression_2 <- df_regression[which(df_regression$First_time==0),]
no1_vector <- c(no1_vector, nrow(df_regression_1))
no2_vector <- c(no2_vector, nrow(df_regression_2))
no3_vector <- c(no3_vector, nrow(df_regression))
  
if (nrow(df_regression_1)>0){
  model1 <- glm(complain_line ~ After_1 + After_2 + Treated + Treated_X_After1 + Treated_X_After2 + ratings + nfriends + useful + funny + cool + elite + nphotos_review + checkin + Fog_index + Avg_word_length + Sent_length + Subjectivity + Polarity, data = df_regression_1, family = "binomial")
  p1_vector_1 <- c(p1_vector_1, coef(summary(model1))['Treated_X_After1','Pr(>|z|)'])
  b1_vector_1 <- c(b1_vector_1, coef(summary(model1))['Treated_X_After1','Estimate'])
  p1_vector_2 <- c(p1_vector_2, coef(summary(model1))['Treated_X_After2','Pr(>|z|)'])
  b1_vector_2 <- c(b1_vector_2, coef(summary(model1))['Treated_X_After2','Estimate'])
  #p1_vector_3 <- c(p1_vector_3, coef(summary(model1))['Treated_X_After3','Pr(>|z|)'])
  #b1_vector_3 <- c(b1_vector_3, coef(summary(model1))['Treated_X_After3','Estimate'])
  r1_vector <- c(r1_vector, with(summary(model1), 1 - deviance/null.deviance))
  v1_vector <- c(v1_vector, toString(names(model.frame(model1))[2:19][summary(model1)$coeff[-1,4] < 0.05]))
} else {
  p1_vector <- c(p1_vector, 0)
  b1_vector <- c(b1_vector, 0)
  r1_vector <- c(r1_vector, 0)
  v1_vector <- c(v1_vector, 0)
}

model2 <- glm(complain_line ~ After_1 + After_2 + Treated + Treated_X_After1 + Treated_X_After2 + ratings + nfriends + useful + funny + cool + elite + nphotos_review + checkin + Fog_index + Avg_word_length + Sent_length + Subjectivity + Polarity, data = df_regression_2, family = "binomial")
model3 <- glm(complain_line ~ After_1 + After_2 + Treated + Treated_X_After1 + Treated_X_After2 + ratings + nfriends + useful + funny + cool + elite + nphotos_review + checkin + Fog_index + Avg_word_length + Sent_length + Subjectivity + Polarity, data = df_regression, family = "binomial")

p2_vector_1 <- c(p2_vector_1, coef(summary(model2))['Treated_X_After1','Pr(>|z|)'])
b2_vector_1 <- c(b2_vector_1, coef(summary(model2))['Treated_X_After1','Estimate'])
p2_vector_2 <- c(p2_vector_2, coef(summary(model2))['Treated_X_After2','Pr(>|z|)'])
b2_vector_2 <- c(b2_vector_2, coef(summary(model2))['Treated_X_After2','Estimate'])
#p2_vector_3 <- c(p2_vector_3, coef(summary(model2))['Treated_X_After3','Pr(>|z|)'])
#b2_vector_3 <- c(b2_vector_3, coef(summary(model2))['Treated_X_After3','Estimate'])
r2_vector <- c(r2_vector, with(summary(model2), 1 - deviance/null.deviance))
v2_vector <- c(v2_vector, toString(names(model.frame(model2))[2:19][summary(model2)$coeff[-1,4] < 0.05]))
p3_vector_1 <- c(p3_vector_1, coef(summary(model3))['Treated_X_After1','Pr(>|z|)'])
b3_vector_1 <- c(b3_vector_1, coef(summary(model3))['Treated_X_After1','Estimate'])
p3_vector_2 <- c(p3_vector_2, coef(summary(model3))['Treated_X_After2','Pr(>|z|)'])
b3_vector_2 <- c(b3_vector_2, coef(summary(model3))['Treated_X_After2','Estimate'])
#p3_vector_3 <- c(p3_vector_3, coef(summary(model3))['Treated_X_After3','Pr(>|z|)'])
#b3_vector_3 <- c(b3_vector_3, coef(summary(model3))['Treated_X_After3','Estimate'])
r3_vector <- c(r3_vector, with(summary(model3), 1 - deviance/null.deviance))
v3_vector <- c(v3_vector, toString(names(model.frame(model3))[2:19][summary(model3)$coeff[-1,4] < 0.05])) 
 
if (nrow(df_regression_1)>0){
  model4 <- glm(complain_service ~ After_1 + After_2 + Treated + Treated_X_After1 + Treated_X_After2 + ratings + nfriends + useful + funny + cool + elite + nphotos_review + checkin + Fog_index + Avg_word_length + Polarity + Subjectivity + Sent_length, data = df_regression_1, family = "binomial")
  p4_vector_1 <- c(p4_vector_1, coef(summary(model4))['Treated_X_After1','Pr(>|z|)'])
  b4_vector_1 <- c(b4_vector_1, coef(summary(model4))['Treated_X_After1','Estimate'])
  p4_vector_2 <- c(p4_vector_2, coef(summary(model4))['Treated_X_After2','Pr(>|z|)'])
  b4_vector_2 <- c(b4_vector_2, coef(summary(model4))['Treated_X_After2','Estimate'])
  #p4_vector_3 <- c(p4_vector_3, coef(summary(model4))['Treated_X_After3','Pr(>|z|)'])
  #b4_vector_3 <- c(b4_vector_3, coef(summary(model4))['Treated_X_After3','Estimate'])
  r4_vector <- c(r4_vector, with(summary(model4), 1 - deviance/null.deviance))
  v4_vector <- c(v4_vector, toString(names(model.frame(model4))[2:19][summary(model4)$coeff[-1,4] < 0.05]))
} else {
  p4_vector <- c(p4_vector, 0)
  b4_vector <- c(b4_vector, 0)
  r4_vector <- c(r4_vector, 0)
  v4_vector <- c(v4_vector, 0)
}

model5 <- glm(complain_service ~ After_1 + After_2 + Treated + Treated_X_After1 + Treated_X_After2 + ratings + nfriends + useful + funny + cool + elite + nphotos_review + checkin + Fog_index + Avg_word_length + Polarity + Subjectivity + Sent_length, data = df_regression_2, family = "binomial")
model6 <- glm(complain_service ~ After_1 + After_2 + Treated + Treated_X_After1 + Treated_X_After2 + ratings + nfriends + useful + funny + cool + elite + nphotos_review + checkin + Fog_index + Avg_word_length + Polarity + Subjectivity + Sent_length, data = df_regression, family = "binomial")
p5_vector_1 <- c(p5_vector_1, coef(summary(model5))['Treated_X_After1','Pr(>|z|)'])
b5_vector_1 <- c(b5_vector_1, coef(summary(model5))['Treated_X_After1','Estimate'])
p5_vector_2 <- c(p5_vector_2, coef(summary(model5))['Treated_X_After2','Pr(>|z|)'])
b5_vector_2 <- c(b5_vector_2, coef(summary(model5))['Treated_X_After2','Estimate'])
#p5_vector_3 <- c(p5_vector_3, coef(summary(model5))['Treated_X_After3','Pr(>|z|)'])
#b5_vector_3 <- c(b5_vector_3, coef(summary(model5))['Treated_X_After3','Estimate'])
r5_vector <- c(r5_vector, with(summary(model5), 1 - deviance/null.deviance))
v5_vector <- c(v5_vector, toString(names(model.frame(model5))[2:19][summary(model5)$coeff[-1,4] < 0.05]))
p6_vector_1 <- c(p6_vector_1, coef(summary(model6))['Treated_X_After1','Pr(>|z|)'])
b6_vector_1 <- c(b6_vector_1, coef(summary(model6))['Treated_X_After1','Estimate'])
p6_vector_2 <- c(p6_vector_2, coef(summary(model6))['Treated_X_After2','Pr(>|z|)'])
b6_vector_2 <- c(b6_vector_2, coef(summary(model6))['Treated_X_After2','Estimate'])
#p6_vector_3 <- c(p6_vector_3, coef(summary(model6))['Treated_X_After3','Pr(>|z|)'])
#b6_vector_3 <- c(b6_vector_3, coef(summary(model6))['Treated_X_After3','Estimate'])
r6_vector <- c(r6_vector, with(summary(model6), 1 - deviance/null.deviance))
v6_vector <- c(v6_vector, toString(names(model.frame(model6))[2:19][summary(model6)$coeff[-1,4] < 0.05]))



result <- data.frame("Period" = period_vector, "Min_num" = min_num_vector, "Measure" = measure_vector, "Observations" = observation_vector, "Formula" = formula_vector,"Ratio" = ratio_vector, "Caliper" = caliper_vector, "P_value(Group1_line_Year1)" = p1_vector_1, "Coefficient(Group1_line_Year1)" = b1_vector_1, "P_value(Group1_line_Year2)" = p1_vector_2, "Coefficient(Group1_line_Year2)" = b1_vector_2, "P_value(Group1_line_Year3)" = p1_vector_3, "Coefficient(Group1_line_Year3)" = b1_vector_3, "Rsquared(Group1_line)" = r1_vector, "P_value(Group2_line_Year1)" = p2_vector_1, "Coefficient(Group2_line_Year1)" = b2_vector_1, "P_value(Group2_line_Year2)" = p2_vector_2, "Coefficient(Group2_line_Year2)" = b2_vector_2, "P_value(Group2_line_Year3)" = p2_vector_3, "Coefficient(Group2_line_Year3)" = b2_vector_3,  "Rsquared(Group2_line)" = r2_vector, "P_value(Group3_line_Year1)" = p3_vector_1, "Coefficient(Group3_line_Year1)" = b3_vector_1, "P_value(Group1_line_Year2)" = p3_vector_2, "Coefficient(Group3_line_Year2)" = b3_vector_2, "P_value(Group1_line_Year3)" = p3_vector_3, "Coefficient(Group3_line_Year3)" = b3_vector_3, "Rsquared(Group3_line)" = r3_vector,"P_value(Group1_service_Year1)" = p4_vector_1,"Coefficient(Group1_service_Year1)" = b4_vector_1, "P_value(Group1_service_Year2)" = p4_vector_2,"Coefficient(Group1_service_Year2)" = b4_vector_2, "P_value(Group1_service_Year3)" = p4_vector_3,"Coefficient(Group1_service_Year3)" = b4_vector_3, "Rsquared(Group1_service)" = r4_vector, 
"P_value(Group2_service_Year1)" = p5_vector_1,"Coefficient(Group2_service_Year1)" = b5_vector_1, "P_value(Group2_service_Year2)" = p5_vector_2,"Coefficient(Group2_service_Year2)" = b5_vector_2, "P_value(Group2_service_Year3)" = p5_vector_3,"Coefficient(Group2_service_Year3)" = b5_vector_3, "Rsquared(Group2_service)" = r5_vector, 
"P_value(Group3_service_Year1)" = p6_vector_1,"Coefficient(Group3_service_Year1)" = b6_vector_1, "P_value(Group3_service_Year2)" = p6_vector_2,"Coefficient(Group3_service_Year2)" = b6_vector_2, "P_value(Group3_service_Year3)" = p6_vector_3,"Coefficient(Group3_service_Year3)" = b6_vector_3, "Rsquared(Group3_service)" = r6_vector, "No_observation_group1"=no1_vector,
"No_observation_group2"=no2_vector, "No_observation_group3"=no3_vector, "Variables_group1_line" = v1_vector, "Variables_group2_line" = v2_vector, "Variables_group3_line" = v3_vector, "Variables_group1_service" = v4_vector, "Variables_group2_service" = v5_vector, "Variables_group3_service" = v6_vector)

write_csv(result, "/Users/aoqu/Desktop/NoWait_Research/PSM+DID/2years_line&service(regression).csv")

```


```{r}
result <- data.frame("Period" = period_vector, "Min_num" = min_num_vector, "Measure" = measure_vector, "Observations" = observation_vector, "Formula" = formula_vector,"Ratio" = ratio_vector, "Caliper" = caliper_vector, "P_value(Group1_line_Year1)" = p1_vector_1, "Coefficient(Group1_line_Year1)" = b1_vector_1, "P_value(Group1_line_Year2)" = p1_vector_2, "Coefficient(Group1_line_Year2)" = b1_vector_2,  "Rsquared(Group1_line)" = r1_vector, "P_value(Group2_line_Year1)" = p2_vector_1, "Coefficient(Group2_line_Year1)" = b2_vector_1, "P_value(Group2_line_Year2)" = p2_vector_2, "Coefficient(Group2_line_Year2)" = b2_vector_2,   "Rsquared(Group2_line)" = r2_vector, "P_value(Group3_line_Year1)" = p3_vector_1, "Coefficient(Group3_line_Year1)" = b3_vector_1, "P_value(Group1_line_Year2)" = p3_vector_2, "Coefficient(Group3_line_Year2)" = b3_vector_2,  "Rsquared(Group3_line)" = r3_vector,"P_value(Group1_service_Year1)" = p4_vector_1,"Coefficient(Group1_service_Year1)" = b4_vector_1, "P_value(Group1_service_Year2)" = p4_vector_2,"Coefficient(Group1_service_Year2)" = b4_vector_2,  "Rsquared(Group1_service)" = r4_vector, 
"P_value(Group2_service_Year1)" = p5_vector_1,"Coefficient(Group2_service_Year1)" = b5_vector_1, "P_value(Group2_service_Year2)" = p5_vector_2,"Coefficient(Group2_service_Year2)" = b5_vector_2,  "Rsquared(Group2_service)" = r5_vector, 
"P_value(Group3_service_Year1)" = p6_vector_1,"Coefficient(Group3_service_Year1)" = b6_vector_1, "P_value(Group3_service_Year2)" = p6_vector_2,"Coefficient(Group3_service_Year2)" = b6_vector_2,  "Rsquared(Group3_service)" = r6_vector, "No_observation_group1"=no1_vector,
"No_observation_group2"=no2_vector, "No_observation_group3"=no3_vector, "Variables_group1_line" = v1_vector, "Variables_group2_line" = v2_vector, "Variables_group3_line" = v3_vector, "Variables_group1_service" = v4_vector, "Variables_group2_service" = v5_vector, "Variables_group3_service" = v6_vector)

write_csv(result, "/Users/aoqu/Desktop/NoWait_Research/PSM+DID/2years_line&service(regression).csv")
```

```{r}
m.out <- matchit(Treated ~Review_count_before + Rating_before, data = new_data, ratio=5, discard="both", method="nearest", exact=c("Match", "City_code"), caliper=0.25)
summary(m.out)
```
```{r}
plot(m.out, type="hist")
```
```{r}
matches = m.out$match.matrix
matches_df = data.frame(cbind(row.names(matches), matches))
```

```{r}
write_csv(match.data(m.out), "/Users/aoqu/Desktop/NoWait_Research/PSM+DID/Third_parties_result.csv")
write_csv(matches_df, "/Users/aoqu/Desktop/NoWait_Research/PSM+DID/Matched_pairs.csv")
```
```{r}
review = read_csv("/Users/aoqu/Desktop/NoWait_Research/PSM+DID/data_did.csv")
```
```{r}
result <- data.frame("Period" = period_vector, "Min_num" = min_num_vector, "Measure" = measure_vector, "Observations" = observation_vector, "Formula" = formula_vector,"Ratio" = ratio_vector, "Caliper" = caliper_vector, "P_value_Group1_line" = p1_vector,"Coefficient_Group1_line" = b1_vector, "Rsquared_Group1_line" = r1_vector,"P_value_Group2_line" = p2_vector, "Coefficient_Group2_line" = b2_vector,"Rsquared_Group2_line" = r2_vector, "P_value_Group3_line" =p3_vector,"Coefficient_Group3_line" = b3_vector, "Rsquared_Group3_line" =r3_vector,"P_value_Group1_service" = p4_vector,"Coefficient_Group1_service" = b4_vector,"Rsquared_Group1_service" = r4_vector, "P_value_Group2_service" = p5_vector,"Coefficient_Group2_service" = b5_vector, "Rsquared_Group2_service" = r5_vector,"P_value_Group3_service" = p6_vector, "Coefficient_Group3_service" = b6_vector,"Rsquared_Group3_service" = r6_vector)
```
```{r}
glm.fit <- glm(complain_line ~ ratings + nfriends, data = review, family = binomial)
summary(glm.fit)
```







```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

